Technical Report

### 2018-03-20 fully-abstract-comp/technical-report.tex
PC-derived code pointers also in trusted value relation.
First write up of code region - still needs some work
Trusted and untrusted versions of lrv and lrr, with superscript parameter.

\[
  \lrr(R)(W) = \left\{ \npair{\stpair{\reg}{\reg}} \middle|
    \begin{array}{l}
      \exists S : (\RegName \setminus (\{\pcreg \} \cup R))\fun \World \ldotp \\
      \quad W = \bigoplus_{r \in (\RegName\setminus (\{\pcreg,\rdata \} \cup R))} S(r) \wedge \\
      \quad \forall r \in \RegName \setminus (\{\pcreg \} \cup R)\ldotp\\
      \qquad\npair{\stpair[.]{\src{\reg_S(r)}}{\reg_T(r)}} \in \lrv(S(r))
    \end{array}
            \right\}
\]
We write $\lrr(W)$ to mean $\lrr(\emptyset)(W)$. That is, if we do not need to exclude extra registers, then we simlpy omit that argument.
% DOMI 18-1-2018: the below remark is obsolete, so I commented it out.
% Where $S\text{ is a separation of $W$}$ means that no two partition share the same ``spatial'' region (whatever that is).
%\dominique{18-1-2018: it might be convenient to exclude $\rdata$ from the $\lrr$ relation by default too. Check if we ever use it with other instantiations of R.}
% Lau 19-01-2018: Added rdata as default.

@@

\[
  \lrvtrusted(W) =
  \begin{array}[t]{l}
    \lrv(W)\cup \\
%
    \left\{ \npair{\left(\arraycolsep=0pt\array{l} \src{\seal{\sigma,\sigma_\baddr,\sigma_\eaddr}},\\ \seal{\sigma,\sigma_\baddr,\sigma_\eaddr} \endarray \right)} 
    \; \middle| \;
    \exists r \in \dom(\pwheap) \ldotp \pwheap(r) =_n \text{TODO: code region for trusted code}
    \right\} \cup \\
  \end{array}
\]

@@

>>>>

\[
  \lrrg{\trust}(R)(W) = \left\{ \npair{\stpair{\reg}{\reg}} \middle|
    \begin{array}{l}
      \exists S : (\RegName \setminus (\{\pcreg \} \cup R))\fun \World \ldotp \\
      \quad W = \bigoplus_{r \in (\RegName\setminus (\{\pcreg,\rdata \} \cup R))} S(r) \wedge \\
      \quad \forall r \in \RegName \setminus (\{\pcreg \} \cup R)\ldotp\\
      \qquad\npair{\stpair[.]{\src{\reg_S(r)}}{\reg_T(r)}} \in \lrvg{\trust}(S(r))
    \end{array}
            \right\}
\]
We write $\lrr(W)$ to mean $\lrr(\emptyset)(W)$. That is, if we do not need to exclude extra registers, then we simply omit that argument.
% DOMI 18-1-2018: the below remark is obsolete, so I commented it out.
% Where $S\text{ is a separation of $W$}$ means that no two partition share the same ``spatial'' region (whatever that is).
%\dominique{18-1-2018: it might be convenient to exclude $\rdata$ from the $\lrr$ relation by default too. Check if we ever use it with other instantiations of R.}
% Lau 19-01-2018: Added rdata as default.

@@

\[
  \lrvtrusted(W) =
  \begin{array}[t]{l}
    \lrv(W)\cup \\
%
    \left\{ \npair{\left(\arraycolsep=0pt\array{l} \src{\seal{\sigma,\sigma_\baddr,\sigma_\eaddr}},\\ \seal{\sigma,\sigma_\baddr,\sigma_\eaddr} \endarray \right)} 
    \; \middle| \;
    \exists r \in \dom(\pwheap) \ldotp \pwheap(r) =_n \text{TODO: code region for trusted code}
    \right\} \cup \\
    \left\{ \npair{\left(\arraycolsep=0pt\array{l} \src{((\perm,\normal),\baddr,\eaddr,\aaddr)},\\ ((\perm,\normal),\baddr,\eaddr,\aaddr) \endarray \right)} \;\middle|\; 
    \begin{array}{l}
      \exists r \in \dom(\pwheap) \ldotp \pwheap(r) =_n \text{TODO: code region for trusted code} \wedge\\
      \perm \sqsubseteq \rx \wedge [\baddr,\eaddr] \subseteq \dom(\var{code})
    \end{array}\right\}
  \end{array}
\]

@@

\[
  \codereg{\ta,\sigma_\baddr,\sigma_\eaddr,\code} \defeq (\pure,*,=,=,H^\mathrm{code} \; \ta \; \sigma_\baddr \; \sigma_\eaddr \; \code,H^\mathrm{code}_\sigma \; \ta \; \sigma_\baddr \; \sigma_\eaddr \; \code)
\]

\[
  H^\mathrm{code} \; \ta \; \sigma_\baddr \; \sigma_\eaddr \; \code \; s \; \hat{W} = \{\npair{(\code,\code)} | \dom(\code) = [\aaddr,\baddr] \tand \code(a) = \seal{\sigma_\baddr,\sigma_\baddr,\sigma_\eaddr}\}
\]
\lau{19-03-2018: Add the link capabilitiy to the above? code in ta?}
\[
  H^\mathrm{code}_\sigma \; \ta \; s \; \sigma \; \hat{W} = 
  \begin{array}[t]{l}
\left\{
    \begin{array}{l}
\left. \npair{\arraycolsep=0pt\left(\array{l}\retptrc(\sigma,((\rx,\lin),\baddr,\eaddr,\aaddr'+\calllen - 1)),\\((\rx,\lin),\baddr,\eaddr,\aaddr)\endarray\right)} \middle| \right. \\
      \\
      \begin{array}{l}
        \decInstr{\code([a',a' + \calllen]-1)} = \overline{\scall{o}{r_1}{r_2}} \tand \\
        \aaddr = \aaddr' + \retoffset \tand \\
        \sigma = \sigma_\baddr + o \tand\\
        \lbrack \baddr, \eaddr \rbrack = \dom(\code) \subseteq \ta
      \end{array}

    \end{array}
      \right\} \uplus \\
\left\{
    \begin{array}{l}
\left. \npair{\arraycolsep=0pt\left(\array{l}\retptrd(\sigma,(\baddr,\eaddr)),\\((\rx,\linear),\baddr,\eaddr,\aaddr)\endarray\right)} \middle| \right. \\
      \\
      \begin{array}{l}
        \exists r \in \dom(\pwpriv[\xi(\hat{W})]) \ldotp \pwpriv[\xi(\hat{W})](r) \nequal (\stareg[(\ms,\ms)]{\spa}, ((\rx,\lin),\baddr',\eaddr',\aaddr')) \tand \\
        \quad \dom(\ms) = [\baddr,\eaddr] \tand\\
        \quad \decInstr{\code([a',a' + \calllen]-1)} = \overline{\scall{o}{r_1}{r_2}} \tand \\
        \quad \aaddr = \aaddr' + \calllen \tand \\
        \quad \sigma = \sigma_\baddr + o \tand\\
        \quad \lbrack \baddr', \eaddr' \rbrack = \dom(\code) \subseteq \ta
      \end{array}
    \end{array}
      \right\} \uplus\\
    \left\{
    \begin{array}{l}
\left. \npair{\arraycolsep=0pt\left(\array{l}
      \sealed{\sigma,\vsc}, \vsc' \endarray\right)} \middle| \right. \\
      \\
      \begin{array}{l}
        \sigma \in [\sigma_\baddr,\sigma_\eaddr] \tand\\
        (\dom(\code) \cup \ta \neq \emptyset \tand \npair{\vsc,\vsc'} \in \lrv \; W) \tor \\
        \text{not a call}
      \end{array}
    \end{array}
      \right\}
  \end{array}
\]
